Clustering and Parameter Estimation for the Popularity Adjusted Block Model

### 2020-07-13 summary.Rmd
finishing up simulations

---
title: "Clustering and Parameter Estimation for the Popularity Adjusted Block Model"
# output: pdf_document
output: html_document
# geometry: "left=1cm,right=1cm,top=1cm,bottom=1.5cm"
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{mathtools}
abstract: |
  this
  is
  an
  abstract
---

@@

import::from(magrittr, `%>%`)
library(plot.matrix)

set.seed(314159)
```

@@

# 1 Introduction

## 1.1 Previous work

# 2 Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph

## 2.1 The popularity adjusted block model (PABM)[^pabm]

[^pabm]: https://arxiv.org/abs/1910.01931

Let $G = (V, E)$ be an undirected, unweighted random graph with corresponding 
affinity matrix $A \in \{0, 1\}^{n \times n}$. Then $A$ is a random matrix 
with corresponding edge probability matrix $P$ such that 
$A_{ij} \stackrel{indep}{\sim} Bernoulli(P_{ij})$ for $i > j$ 
($A_{ji} = A_{ij}$ and $A_{ii} = 0$). Let there exist $K$ underlying 
communities in $G$, and let $n_{k}$ be the size of the $k$^th^ community in 
$G$ such that $\sum_{k=1}^K n_k = n$.

@@

## 2.2 The generalized random dot product graph (GRDPG)[^grdpg]

[^grdpg]: https://arxiv.org/abs/1709.05506

Let $X \in \mathbb{R}^{n \times d}$ be latent positions of the vertices of a 
graph $G$. $X$ consists of row vectors $x_i^\top$. Let 
$A \in \{0, 1\}^{n \times n}$ be the corresponding affinity matrix.

@@

## 2.3 Connecting the PABM to the GRDPG for $K = 2$

Let $X = \begin{bmatrix} 
\lambda^{(11)} & \lambda^{(12)} & 0 & 0 \\ 
0 & 0 & \lambda^{(21)} & \lambda^{(22)} 
\end{bmatrix}$ and 
$Y = \begin{bmatrix} \lambda^{(11)} & 0 & \lambda^{(12)} & 0 \\
0 & \lambda^{(21)} & 0 & \lambda^{(22)} \end{bmatrix}$. 
Then $P = X Y^\top$.

@@

## 2.4 Generalization to $K > 2$

Let $\Lambda^{(k)} = 
\begin{bmatrix} \lambda^{(k,1)} & \cdots & \lambda^{(k, K)} \end{bmatrix}
\in [0, 1]^{n_k \times K}$.  
Let $X$ be a block diagonal matrix 
$X = \diag(\Lambda^{(1)}, ..., \Lambda^{(K)}) \in [0, 1]^{n \times K^2}$.

Let $L^{(k)}$ be a block diagonal matrix of column vectors $\lambda^{(lk)}$ for 
$l = 1, ..., K$. $L^{(k)} = \diag(\lambda^{(1k)}, ..., \lambda^{(Kk)}) \in 
[0, 1]^{n \times K}$.  
Let $Y = \begin{bmatrix} L^{(1)} & \cdots & L^{(K)} \end{bmatrix} \in 
[0, 1]^{n \times K^2}$.

Then $P = X Y^\top$.

Similar to the $K = 2$ case, we again have $Y = X \Pi$ for a permutation matrix
$\Pi$, so $P = X \Pi X^\top$.

The permutation described by $\Pi$ has $K$ fixed points, which correspond to 
$K$ eigenvalues equal to $1$ with corresponding eigenvectors $e_k$ where 
$k = r (K + 1) + 1$ for $r = 0, ..., K - 1$. It also has 
$\binom{K}{2} = K (K - 1) / 2$ cycles of order $2$. Each cycle corresponds to 
a pair of eigenvalues $+1$ and $-1$ and a pair of eigenvectors 
$(e_s + e_t) / \sqrt{2}$ and $(e_s - e_t) / \sqrt{2}$[^pairs].

[^pairs]: TODO: describe pairs $(s, t)$ in more elegant/succinct closed form

@@

**Example: $K = 3$**

Using the same notation as before:

@@

Then $P = X Y$ and $Y = X \Pi$ where 
$\Pi = \begin{bmatrix} 
1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1
\end{bmatrix}$

Perhaps a simpler way to look at this is:

@@

# 3 Methodology

@@

Here, we will focus more on (1) and pose possible methods for (2). In our 
methods, we assume that $K$, the number of clusters, is known beforehand.

## 3.1 Cluster membership identification

### 3.1.1 Using edge probability matrix $P$

We previously stated one possible set of latent positions that result in the 
edge probability matrix of a PABM, $P = (XU) I_{pq} (XU)^\top$. If we have 
(or can estimate) $XU$ directly, then both the clustering and parameter 
identification problem are trivial since $U$ is orthonormal and fixed for each 
value of $K$. However, direct identification or estimation of $XU$ is not 
possible.

@@

We can note from the explicit form of $XU$ that it represents points in 
$\mathbb{R}^{K^2}$ such that points within each cluster lie on $K$-dimensional 
subspaces. Furthermore, the subspaces are orthogonal to each other. 
Multiplication by $Q \in \mathbb{O}(p, q)$ removes the orthogonality property 
but retains the property that each cluster is represented by a $K$-dimensional 
subspace. Using this property, previous work proposes the use of subspace 
clustering while acknowledging some of its shortcomings.

**Theorem 1.** 
*Let $P = V D V^\top$ be the spectral decomposition of the edge probability
matrix.*

### 3.1.2 Using adjacency matrix $A$

## 3.2 Parameter estimation

# 4 Simulated Examples

>>>>

---
title: "Clustering and Parameter Estimation for the Popularity Adjusted Block Model"
# output:
#   pdf_document:
#     citation_package: natbib
#     number_sections: yes
output: html_document
# geometry: "left=1cm,right=1cm,top=1cm,bottom=1.5cm"
urlcolor: blue
header-includes:
- \usepackage{float}
- \usepackage{mathtools}
- \usepackage{natbib}
- \usepackage[linesnumbered,vlined,ruled]{algorithm2e} 
- \setcitestyle{numbers,square}
bibliography: misc.bib
abstract: |
  In this paper, we connect two probabolistic models for graphs, the Popularity 
  Adjusted Block Model (PABM) and the Generalized Random Dot Product Graph 
  (GRDPG) and use properties established in this connection to aid in 
  clustering and parameter estimation. In particular, we note that the PABM 
  can be represented as latent positions such that points within the same 
  cluster lie on a subspace, and the subspaces that represent different 
  clusters are orthogonal to one another. Using this property as well as the 
  asymptotic properties of Adjacency Spectral Embedding of the GRDPG, we are 
  able to establish theoretical asymptotic results of our clustering and 
  parameter estimation methods for the PABM.
---

@@

import::from(magrittr, `%>%`)
import::from(foreach, foreach, `%do%`)
library(plot.matrix)
library(mclust)
library(ggplot2)

set.seed(314159)

source('http://pages.iu.edu/~mtrosset/Courses/675/stress.r')

doMC::registerDoMC(parallel::detectCores())

embedding <- function(A, p = NULL, q = NULL,
                      eps = 1e-6) {
  eigen.A <- eigen(A, symmetric = TRUE)
  if (is.null(p) | is.null(q)) {
    keep <- (abs(eigen.A$values) > eps)
  } else {
    keep <- c(seq(p), seq(n, n - q + 1))
  }

  U <- eigen.A$vectors[, keep]
  S <- diag(sqrt(abs(eigen.A$values[keep])))
  return(U %*% S)
}

draw.graph <- function(P) {
  A <- apply(P, 1:2, function(p) rbinom(1, 1, p))
  A[lower.tri(A)] <- 0
  diag(A) <- 0
  A <- A + t(A)
  return(A)
}
```

@@

# Introduction

The Popularity Adjusted Block Model (PABM) was introduced by 
\citet*{307cbeb9b1be48299388437423d94bf1} as a generalization of the Stochastic 
Block Model (SBM) to address the heterogeneity of edge probabilities within and 
between communities or clusters.

## Previous work

\citet*{noroozi2019estimation} proposed using sparse subspace clustering (SSC) 
to identify the cluster memberships given either an edge probability matrix $P$ 
or an adjacency matrix $A$. In the case that $P$ is known, the cluster 
memberships can be identified exactly (up to permutation). A similar procedure 
can be applied if $P$ is unknown and we have an observation $A$, but the 
theoretical guarantees of this method applied to the PABM are unknown. In 
particular, the method requires spherical Gaussian noise. The authors of this 
paper then use point estimators for $\{\lambda^{(kl)}\}$ with the results of 
SSC.

# Connecting the Popularity Adjusted Block Model to the Generalized Random Dot Product Graph

## The popularity adjusted block model (PABM) \cite{noroozi2019estimation}

**Definition 1**
Let $G = (V, E)$ be an undirected, unweighted random graph with corresponding 
affinity matrix $A \in \{0, 1\}^{n \times n}$. Then $A$ is a random matrix 
with corresponding edge probability matrix $P$ such that 
$A_{ij} \stackrel{indep}{\sim} Bernoulli(P_{ij})$ for $i > j$ 
($A_{ji} = A_{ij}$ and $A_{ii} = 0$). Let there exist $K$ underlying 
communities in $G$, and let $n_{k}$ be the size of the $k$^th^ community in 
$G$ such that $\sum_{k=1}^K n_k = n$.

@@

## The generalized random dot product graph (GRDPG) \cite{rubindelanchy2017statistical}

**Definition 2**
Let $X \in \mathbb{R}^{n \times d}$ be latent positions of the vertices of a 
graph $G$. $X$ consists of row vectors $x_i^\top$. Let 
$A \in \{0, 1\}^{n \times n}$ be the corresponding affinity matrix.

@@

## Connecting the PABM to the GRDPG

### Case where $K = 2$

**Theorem 1**. 
Let $X = \begin{bmatrix} 
\lambda^{(11)} & \lambda^{(12)} & 0 & 0 \\ 
0 & 0 & \lambda^{(21)} & \lambda^{(22)} 
\end{bmatrix}$ 
where the $\lambda^{(kl)}$'s are defined as in Definition 1 for $K=2$, and 
let $U = \begin{bmatrix} 1 & 0 & 0 & 0 \\
0 & 0 & 1 / \sqrt{2} & 1 / \sqrt{2} \\
0 & 0 & 1 / \sqrt{2} & - 1 / \sqrt{2} \\
0 & 1 & 0 & 0 \end{bmatrix}$. 
Then $A \sim GRDPG_{3, 1}(3, 1)$ and $A \sim PABM(\{(\lambda^{(kl)}\}_K)$ are 
equivalent.

*Proof*.
Let $X = \begin{bmatrix} 
\lambda^{(11)} & \lambda^{(12)} & 0 & 0 \\ 
0 & 0 & \lambda^{(21)} & \lambda^{(22)} 
\end{bmatrix}$ and 
$Y = \begin{bmatrix} \lambda^{(11)} & 0 & \lambda^{(12)} & 0 \\
0 & \lambda^{(21)} & 0 & \lambda^{(22)} \end{bmatrix}$. 
Then $P = X Y^\top$.

@@

### Generalization to $K > 2$

**Theorem 2**. There exists a block diagonal matrix 
$X \in \mathbb{R}^{n \times K^2}$ defined by PABM parameters 
$\{\lambda^{(kl)}\}_K$ and $U \in \mathbb{R}^{K^2 \times K^2}$ that is fixed 
for each $K$ such that $A \sim GRDPG_{K (K+1) / 2, K (K-1) / 2}(XU)$ and 
$A \sim PABM(\{(\lambda^{(kl)}\})_K)$ are equivalent.

*Proof*
Let $\Lambda^{(k)} = 
\begin{bmatrix} \lambda^{(k,1)} & \cdots & \lambda^{(k, K)} \end{bmatrix}
\in [0, 1]^{n_k \times K}$.  
Let $X$ be a block diagonal matrix 
$X = \diag(\Lambda^{(1)}, ..., \Lambda^{(K)}) \in [0, 1]^{n \times K^2}$.  
Let $L^{(k)}$ be a block diagonal matrix of column vectors $\lambda^{(lk)}$ for 
$l = 1, ..., K$. $L^{(k)} = \diag(\lambda^{(1k)}, ..., \lambda^{(Kk)}) \in 
[0, 1]^{n \times K}$.  
Let $Y = \begin{bmatrix} L^{(1)} & \cdots & L^{(K)} \end{bmatrix} \in 
[0, 1]^{n \times K^2}$.  
Then $P = X Y^\top$.  
Similar to the $K = 2$ case, we again have $Y = X \Pi$ for a permutation matrix
$\Pi$, so $P = X \Pi X^\top$.  
The permutation described by $\Pi$ has $K$ fixed points, which correspond to 
$K$ eigenvalues equal to $1$ with corresponding eigenvectors $e_k$ where 
$k = r (K + 1) + 1$ for $r = 0, ..., K - 1$. It also has 
$\binom{K}{2} = K (K - 1) / 2$ cycles of order $2$. Each cycle corresponds to 
a pair of eigenvalues $+1$ and $-1$ and a pair of eigenvectors 
$(e_s + e_t) / \sqrt{2}$ and $(e_s - e_t) / \sqrt{2}$.

@@

**Example** for $K = 3$. Using the same notation as before:

@@

Then $P = X Y^\top$ and $Y = X \Pi$ where 
$\Pi = \begin{bmatrix} 
1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 & 0 \\
0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 1 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & 0 & 1 & 0 \\
0 & 0 & 1 & 0 & 0 & 0 & 0 & 0 & 0 \\
0 & 0 & 0 & 0 & 0 & 0 & 0 & 0 & 1
\end{bmatrix}$

Another way to look at this is:

@@

# Methods

@@

Here, we will focus more on (1) and pose possible methods for (2). In our 
methods, we assume that $K$, the number of clusters, is known beforehand and 
does not require estimation.

## Clustering

### Using edge probability matrix $P$

We previously stated one possible set of latent positions that result in the 
edge probability matrix of a PABM, $P = (XU) I_{pq} (XU)^\top$. If we have 
(or can estimate) $XU$ directly, then both the clustering and parameter 
identification problem are trivial since $U$ is orthonormal and fixed for each 
value of $K$. However, direct identification or estimation of $XU$ is not 
possible \cite{rubindelanchy2017statistical}.

@@

We can note from the explicit form of $XU$ that it represents points in 
$\mathbb{R}^{K^2}$ such that points within each cluster lie on $K$-dimensional 
subspaces. Furthermore, the subspaces are orthogonal to each other. 
Multiplication by $Q \in \mathbb{O}(p, q)$ removes the orthogonality property 
but retains the property that each cluster is represented by a $K$-dimensional 
subspace. Using this property, previous work proposes the use of subspace 
clustering while acknowledging some of its shortcomings 
\cite{noroozi2019estimation} \cite{soltanolkotabi2014}.

**Theorem 3.** 
Let $P = V D V^\top$ be the spectral decomposition of the edge probability
matrix. Let $B = V V^\top$. Then $B_{ij} = 0$ if vertices $i$ and $j$ are 
of different clusters.

*Proof (sketch)*
By projection, $V V^\top = X (X^\top X)^{-1} X^\top$ where $X$ is defined as 
in Theorem 2. Since $X$ is block diagonal with each block corresponding 
to one cluster, $X (X^\top X)^{-1} X^\top$ is also a block diagonal matrix 
with each block corresponding to a cluster and zeros elsewhere. Therefore, 
if vertices $i$ and $j$ belong to different clusters, then the $ij$^th^ element 
of $X (X^\top X)^{-1} X^\top = V V^\top = B$ is 0.

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \KwData{Edge probability matrix $P$, number of clusters $K$}
  \KwResult{Cluster assignments $1, ..., K$}
    Compute the spectral decomposition $P = V D V^\top$\;
    Compute the inner product matrix $B = V V^\top$\;
    Identify the connected components and map each to clusters $1..K$\;
  \caption{PABM clustering on the edge probability matrix}
\end{algorithm}

### Using adjacency matrix $A$

The adjacency embedding of $A$ approaches latent positions that form $P$ as 
the number of vertices $n$ increases. More 
precisely, let $\{\lambda^{(kl)}\}_K \sim \mathcal{F}_K$ for some joint 
distribution consisting of $K$ underlying clusters $\mathcal{F}_K$. Then the 
latent positions $XU \sim \mathcal{G}_K$ for some related joint distribution 
with $K$ underlying clusters $\mathcal{G}_K$. Denote $Z_n$ as a sample of size 
$n$ from $\mathcal{G}_K$ and adjacency matrix $A_n$ as one draw from edge 
probability matrix $P_n = Z_n I_{pq} Z_n^\top$. Let $\hat{Z}_n$ be the 
adjacency embedding of $A_n$ with rows $(\hat{z}_i^{(n)})^\top$. Then by
\citet*{rubindelanchy2017statistical},

$$\max\limits_{i \in \{1, ..., n\}} ||Q_n \hat{z}_i^{(n)} - z_i^{(n)}|| = O_P\bigg(\frac{(\log n)^c}{n^{1/2}} \bigg)$$

for some $c>0$ and sequence of $Q_n \in \mathbb{O}(p, q)$. In addition, 
\citeauthor{rubindelanchy2017statistical} produce a central limit theorem 
result.

**Theorem 4**. Let $\hat{V}^{(n)} \in \mathbb{R}^{n \times K^2}$ be the matrix 
of $K^2$ eigenvectors of $A_n$ corresponding to the $K (K+1) / 2$ most positive 
eigenvalues and $K (K-1) / 2$ most negative eigenvalues with rows
$(\hat{v}_i^{(n)})^\top$. Let $(i, j)$ correspond to pairs belonging to 
different clusters. Then for some $c > 0$,

$$\max\limits_{i, j} ||(\hat{v}^{(n)}_i)^\top \hat{v}_j^{(n)}|| = O_P\bigg( \frac{(\log n)^c}{n}\bigg)$$

In addition, $(\hat{v}^{(n)}_i)^\top \hat{v}_j^{(n)}$ converge to a generalized 
chi-square distribution.

\begin{algorithm}[H]
  \DontPrintSemicolon
  \SetAlgoLined
  \KwData{Adjacency matrix $A$, number of clusters $K$}
  \KwResult{Cluster assignments $1, ..., K$}
    Compute the eigenvectors of $A$ that correspond to the $K (K+1) / 2$ most 
    positive eigenvalues and $K (K-1) / 2$ most negative eigenvalues. Construct 
    $V$ using these eigenvectors as its columns.\;
    Compute $B = V V^\top$.\;
    Construct graph $G$ using $B$ as its similarity matrix.\;
    Partition $G$ into $K$ disconnected components 
    (e.g., using edge thresholding or spectral clustering).\;
    Map each connected components as the clusters $1, ..., K$.\;
  \caption{PABM clustering on the adjacency matrix}
\end{algorithm}

## Parameter estimation

For this section, we will focus on the case $K = 2$. Under this condition, the 
PABM is equivalent to the GRDPG with signature $(3, 1)$.

The adjacency spectral embeddings of both $A$ and $P$ are not unique. In 
particular, let $Z$ be the ASE of $P$. Then $P = Z I_{3, 1} Z^\top$. However, 
for any $Q \in \mathbb{O}(3, 1)$, 
$(ZQ) I_{3, 1} (ZQ)^\top = Z (Q I_{3, 1} Q^\top) Z^\top = Z I_{3, 1} Z^\top = P$,
so $ZQ$ is also a valid ASE Of $P$. If we can find $Q \in \mathbb{O}(3, 1)$ 
such that $ZQ = XU$, we can compute the parameters $\{\lambda^{(kl)}\}$ 
directly. Furthermore, if we instead use the ASE of the adjacency matrix $A$, 
$\exists Q \in \mathbb{O}(3, 1)$ such that $\max\limits_i ||Q \hat{z}_i - XU||$ 
is minimized (and goes to zero under a probabolistic model for
$\{\lambda^{(kl)}\}$'s).

Thus if we can identify $Q$ such that the $ZQ = XU$ in the case of embedding 
$P$ or $\hat{Z} Q - XU$ is minimized in the case of embedding $A$, we can 
identify or estimate the PABM parameters directly from the embedding. $XU$ is 
unknown, but we can still obtain an embedding $ZQ$ that follows the properties 
of $XU$, which will yield estimates $\{\hat{\lambda}^{(kl)}\}$ that are valid 
in that they will produce the edge probability matrix $P$.[^lambdas]

[^lambdas]: Note that the set $\{\lambda^{(kl)}\}_K$ that produces a unique 
$P$ is not unique \citep{noroozi2019estimation}.

In particular, we can note the following properties of $XU$:

1. If row $i$ is in cluster 1, then its second index is 0. If it is in cluster 
2, its first index is 0.
2. If row $i$ is in cluster 1, then its third and fourth indices are equal. If 
it is in cluster 2, the fourth index is the negative of its third index.
3. If rows $i$ and $j$ are in different clusters, their dot product is 0.

If we have cluster memberships (either known *a priori* or estimated using a 
clustering method), then we can estimate $XU$ by picking
$Q \in \mathbb{O}(3, 1)$ such that $ZQ$ best fits these properties.

$\mathbb{O}(3, 1)$ happens to be the Lorentz group, and each 
$Q \in \mathbb{O}(3, 1)$ can be represented as the product of six matrices that 
depend on a total of four parameters \cite{10.1088/978-1-6817-4254-0}. This 
lends itself as an optimization problem:

$$\begin{split}
  \min_{\theta, \phi, \psi, \tau} & ||\xi^{(1, 1)}||^2 + ||\xi^{(2, 2)}||^2 + ||\xi^{(1, 3)} - \xi^{(1, 4)}||^2 + ||\xi^{(2, 3)} + \xi^{(2, 4)}||^2 \\
  \text{s.t. } & \Xi = Z Q(\theta, \phi, \psi, \tau) \\
  & \xi^{(i, j)} \text{ is the } j^{th} \text{ column of } \Xi \text{ with rows from the } i^{th} \text{ cluster}
\end{split}$$

Note that if $Q$ can be properly estimated, the asymptotic results from 
\citet{rubindelanchy2017statistical} can be applied here.

# Simulated Examples

For these examples, we will set the following parameters:

* $K = 2$
* Mixture parameter $\alpha = .5$
* $\lambda^{(kk)} \stackrel{indep}{\sim} Beta(2, 1)$
* $\lambda^{(kl)} \stackrel{indep}{\sim} Beta(1, 2)$ for $k \neq l$

```{r}
K <- 2
p <- K * (K + 1) / 2
q <- K * (K - 1) / 2
alpha <- .5
a1 <- 2
b1 <- 1
a2 <- 1
b2 <- 2
```

## Clustering

In this part, we will assess Algorithm 1's performance for sample sizes 
$n = 64, 128, 256, 512, 1024$. For each sample size $n$, $100$ sets of 
$\lambda^{(kl)}$'s are drawn and for each set of parameters, one adjacency 
matrix $A$ is drawn and clustered.

```{r}
n.vec <- c(64, 128, 256, 512, 1024)
iter <- 100
```

```{r}
draw.pabm.beta.2 <- function(n, a1, b1, a2, b2, alpha = .5) {
  z <- sample(c(1, 2), n, prob = c(alpha, 1 - alpha), replace = TRUE)
    z <- sort(z)

    n1 <- sum(z == 1)
    n2 <- sum(z == 2)

    lambda11 <- rbeta(n1, a1, b1)
    lambda22 <- rbeta(n2, a1, b1)
    lambda12 <- rbeta(n1, a2, b2)
    lambda21 <- rbeta(n2, a2, b2)

    X <- cbind(c(lambda11, rep(0, n2)),
               c(lambda12, rep(0, n2)),
               c(rep(0, n1), lambda21),
               c(rep(0, n1), lambda22))
    Y <- cbind(c(lambda11, rep(0, n2)),
               c(rep(0, n1), lambda21),
               c(lambda12, rep(0, n2)),
               c(rep(0, n1), lambda22))
    P <- X %*% t(Y)
    A <- draw.graph(P)

    return(list(A = A, z = z))
}

normalized.laplacian <- function(W) {
  n <- nrow(W)
  D.neg.sqrt <- diag(colSums(W) ** -.5)
  I <- diag(n)
  return(I - D.neg.sqrt %*% W %*% D.neg.sqrt)
}

cluster.pabm <- function(A, K) {
  p <- K * (K + 1) / 2
  q <- K * (K - 1) / 2
  V <- eigen(A, symmetric = TRUE)$vectors[, c(seq(p), seq(n, n - q + 1))]
  V <- V / mean(V)
  B <- abs(V %*% t(V))
  # L <- graph.laplacian(B)
  L <- normalized.laplacian(B)
  eigenmap <- eigen(L, symmetric = TRUE)$vectors[, seq(n - 1, n - K)]
  clustering <- mclust::Mclust(eigenmap, K)$classification
}
```

```{r}
results.df <- foreach(n = n.vec,.combine = dplyr::bind_rows) %do% {
  plyr::ldply(seq(iter), function(i) {
    Az <- draw.pabm.beta.2(n, a1, b1, a2, b2, alpha)
    A <- Az$A
    z <- Az$z
    clustering <- cluster.pabm(A, K)
    accuracy <- mean(clustering == z)
    if (accuracy < .5) accuracy <- 1 - accuracy
    dplyr::tibble(n = n, accuracy = accuracy) %>% 
      return()
  }, .parallel = TRUE) %>% 
    return()
}

results.df %>% 
  dplyr::group_by(n) %>% 
  dplyr::summarise(mean.acc = mean(accuracy),
                   sd.acc = sd(accuracy)) %>% 
  ggplot() + 
  labs(y = 'accuracy') + 
  geom_line(aes(x = n, y = mean.acc)) + 
  geom_errorbar(aes(x = n, ymin = mean.acc - sd.acc, ymax = mean.acc + sd.acc))
```

## Parameter estimation

# References
